## Functional tools for R

This module provides a basic toolbox for working with functions in R.

```{r}
box::use(klmr/fun)
```

### Creating functions

Use `closure` to create a function:

```{r}
twice = fun$closure(alist(x =), quote(x * 2), globalenv())
twice
twice(10)
```

### Function composition

Use `compose` to compose functions:

```{r}
four_times = fun$compose(twice, twice)
four_times(2)
```

Alternatively, use one of the function composition operators:

```{r}
box::use(klmr/fun[...]) # Attach module to use operators.

# Traditional order of arguments, same as `compose`:
sd1 = sqrt %.% var
sd1(CO2$uptake)

# Alternative order:
sd2 = var %|>% sqrt
sd2(CO2$uptake)
```

### Function chaining

As made popular by ‘magrittr’ and ‘dplyr’:

```{r}
CO2$uptake %>% var() %>% sqrt()
```

Note the similarity in usage between `%>%` and `%|>%`.

### Partial function application

Partial function application via `partial` creates a new function with fewer
arguments.

```{r}
box::use(klmr/fun[p = partial])
```

```{r}
minus1 = p(`-`, 1)
sapply(1 : 5, minus1)
```

These higher-order functions become powerful when combined, and easily construct
complex anonymous functions.

```{r}
strrev =
    p(strsplit, '') %|>%
    p(lapply, rev) %|>%
    p(lapply, p(paste, collapse = '')) %|>%
    unlist
strrev(c('foo', 'bar'))
```

### A concise lambda syntax

```{r}
box::use(klmr/fun/lambda[...])

sapply(1 : 4, x -> 2 * x)
mapply(x ~ y -> x + y, 1 : 4, 5 : 8)
```

* `var -> expr` is equivalent to `function (var) expr`.

* `x ~ y -> expr` is equivalent to `function (x, y) expr`. An arbitrary number
  of arguments is supported.

**Note:** Importing this submodule changes the semantics of `<-` (since `<-` and
`->` refer to the same operator in R). Consequently, this module can only be
used in code that uses `=` for assignment.
